Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2024-01-04 demystify.tex
updates

\subsection*{References}
\begin{itemize}
\item \href{http://www.pl-enthusiast.net/2022/10/03/how-to-write-a-grad-school-personal-statement/}{How to Write a Grad School Personal Statement} by Mike Hicks
\end{itemize}
% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

\subsubsection*{References}
\begin{itemize}
    \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive "what do I ask/look for" in a PhD Advisor Guide}
\end{itemize}
\subsection{Types of Faculty: Who can serve as a PhD adviser?}\label{sec:faculty-types}

@@

\subsubsection*{References}
\begin{itemize}
    \item \href{https://yonatanbisk.com/emailing_professors.html}{A Note about Emailing Professors} by Yonatan Bisk
\end{itemize}

@@

However, if your goal is a PhD in CS, then you likely need to be in the CS dept \emph{and} advised by a CS faculty. In fact, if a faculty is not in CS, it is unlikely that they can be the \emph{main} adviser of a CS PhD student. They may \emph{co-advise} or be in the PhD dissertation committee, but your main adviser will need to be a tenured or tenure-track faculty in CS. If in doubt, you should check with the CS department for their requirements.  For this specific reason,  CSRankings includes only tenure line faculty who can advise CS PhD students. I also have compiled a \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{list} of Vietnamese faculty who can advise PhD students.

@@

%\chapter{References}

@@

\section{Accepting, Postponing, and Rejecting Offers}

@@

\paragraph{Rejecting an offer} If you decide to reject an offer, you can say something like: \emph{``Thank you for the offer.  I am very excited about it.  However, I have decided to accept another offer.  I appreciate your time and consideration.  I hope we can work together in the future.''}  Professors will understand and will likely wish you good luck.  If you decide to reject an offer, you should do so quickly.

>>>>

\subsection*{Additional Resources}
\begin{itemize}
\item \href{http://www.pl-enthusiast.net/2022/10/03/how-to-write-a-grad-school-personal-statement/}{How to Write a Grad School Personal Statement} by Mike Hicks
\end{itemize}
% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

\subsubsection*{Additional Resources}
\begin{itemize}
    \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive "what do I ask/look for" in a PhD Advisor Guide}
\end{itemize}
\subsection{Types of Faculty: Who can serve as a PhD adviser?}\label{sec:faculty-types}

@@

\subsubsection*{Additional Resources}
\begin{itemize}
    \item \href{https://yonatanbisk.com/emailing_professors.html}{A Note about Emailing Professors} by Yonatan Bisk
    \item \S\ref{sec:accept-postpone-decline} How to accept/postpone/decline PhD offers (and do it gracefully)
\end{itemize}

@@

However, if your goal is a PhD in CS, then you likely need to be in the CS dept \emph{and} advised by a CS faculty. In fact, if a faculty is not in CS, it is unlikely that they can be the \emph{main} adviser of a CS PhD student. They may \emph{co-advise} or be in the PhD dissertation committee, but your main adviser will need to be a tenured or tenure-track faculty in CS. If in doubt, you should check with the CS department for their requirements.  For this specific reason,  CSRankings includes only tenure line faculty who can advise CS PhD students. I also have compiled a \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{list} of Vietnamese faculty who can advise PhD students. \S\ref{sec:faculty-types} talks more about who can serve as your PhD adviser.

@@

%\chapter{Additional Resources}

@@

\section{Accepting, Postponing, and Decline Offers}\label{sec:accept-postpone-decline}

@@

\paragraph{Declining an offer} If you decide to decline or reject an offer, you can say something like: \emph{``Thank you for the offer.  I am very excited about it.  However, I have decided to accept another offer.  I appreciate your time and consideration.  I hope we can work together in the future.''}  Professors will understand and will likely wish you good luck.  If you decide to reject an offer, you should do so quickly.
